### 2017-01-17 second-order-spsa-3.tex
sir corrections first intro only
sir corrections 2,3chap only
counter conditions problem resoved

 \chapter{Second-order SPSA with improved hessian estimation (2SPSA-3-IH)}
\label{sec:2spsa-3-ih}
The second-order SPSA-3 with improved Hessian estimate performs an update iteration similar to that of 2RDSA-IH proposed in section \ref{sec:2rdsa-ih} (See \eqref{eq:e2rdsa} and \eqref{eq:2rdsa-H}). The main difference in the iterates is that 2SPSA-3-IH uses gradient and Hessian estimates according to \eqref{eq:grad-spsa} and \eqref{eq:2spsa-ber}. In this section we present the improvements to 2SPSA-3 Hessian recursion \eqref{eq:2spsa-3-ih} by incorporating the zero-mean feedback term and general step-size. Note that though these ideas of improving the Hessian recursion is similar to the ideas presented in section \ref{sec:2rdsa-ih} for 2RDSA-IH, the derivation of feedback term does not follow from it. We show that the proposed improvements to Hessian estimation in 2SPSA-3 are such  that the resulting 2SPSA-3-IH algorithm is provably convergent, in particular, the Hessian estimate $\overline H_n$ of 2SPSA-3-IH converges almost surely to the true Hessian. Moreover, we show, for the special case of a quadratic objective in noise-free setting, that 2SPSA-3 scheme along with proposed improvement to Hessian estimation (henceforth referred to as 2SPSA-3-IH) results in a convergence rate that is on par with the corresponding rate for 2SPSA with Hessian estimation improvements (2SPSA-IH) \cite{spall-jacobian}. The advantage with 2SPSA-3-IH is that it requires only 75\% of the simulation cost per-iteration for 2SPSA-IH.

@@

Algorithm \ref{alg:spsa-3-ih-structure} presents the pseudocode and we describe the individual component of 2SPSA-3-IH below.
\section{Function evaluations}
Let $y_n$, $y_n^+$ and $y_n^-$ denote the function evaluations at $\theta_n$, $\theta_n+\delta_n \Delta_n+\delta_n \widehat \Delta_n$ and $\theta_n -\delta_n\Delta_n-\delta_n\widehat\Delta_n$ respectively, i.e., 
$y_n = f(\theta_n) + \xi_n$, $y_n^+ = f(\theta_n+\delta_n \Delta_n +\delta_n \widehat\Delta_n) + \xi_n^+$ and 
$y_n^- = f(\theta_n -\delta_n\Delta_n-\delta_n\widehat\Delta_n) + \xi_n^-$,
where the noise terms $\xi_n, \xi_n^+, \xi_n^-$ satisfy $\E\left[\left.\xi_n^+ + \xi_n^- - 2\xi_n \right| \F_n, \Delta_n, \widehat \Delta_n\right] = 0$ with $\F_n = \sigma(\theta_m,m <  n)$ denoting the underlying sigma-field.

@@

\section{Convergence analysis for 2SPSA-3-IH}
\label{sec:2spsa-results}
We make the same assumptions as those used in the analysis of \cite{prashanth2015rdsa}, with a few minor alterations. The assumptions are listed below:
\begin{enumerate}[label=(\textbf{C\arabic*}),resume]
\item  The function
$f$ is four-times differentiable\footnote{Here $\nabla^4 f(\theta) = \dfrac{\partial^4 f (\theta)}{\partial \theta\tr \partial \theta\tr \partial \theta\tr \partial \theta\tr}$ denotes the fourth derivate of $f$ at $\theta$ and $\nabla^4_{i_1 i_2 i_3 i_4} f(\theta)$ denotes the $(i_1 i_2 i_3 i_4)$th entry of $\nabla^4 f(\theta)$, for $i_1, i_2, i_3,i_4=1,\ldots, N$.} with $\left|\nabla^4_{i_1 i_2 i_3 i_4} f(\theta) \right| < \infty$, for $i_1, i_2, i_3,i_4=1,\ldots, N$ and for all $\theta\in \R^N$.

@@

\item For any $\tau >0$ and nonempty $S \subseteq \{1,\ldots,N\}$, there exists a $\rho'(\tau,S)>\tau$ such that 
$$ \limsup_{n\rightarrow \infty} \left| \dfrac{\sum_{i \notin S} (\theta-\theta^*)_i \bar f_{ni}(\theta)}{\sum_{i \in S} (\theta-\theta^*)_i \bar f_{ni}(\theta)}               \right| < 1 \text{ a.s.}$$
for all $|(\theta-\theta^*)_i| < \tau$ when $i \notin S$ and $|(\theta-\theta^*)_i| \ge \rho'(\tau,S)$ when $i\in S$.
\item For some $\alpha_0, \alpha_1, \alpha_2 >0$ and for all $n,l,m$, $\E {\xi_n}^{2} \le \alpha_0$, $\E {\xi_n^{\pm}}^{2} \le \alpha_0$, $\E f(\theta_n)^{2} \le \alpha_1$,  $\E f(\theta_n + \delta_n \Delta_n + \delta_n \widehat \Delta_n)^{2},\E f(\theta_n - \delta_n \Delta_n - \delta_n \widehat \Delta_n)^{2} \le \alpha_1$, 
%$\E \left[ f(\theta_n + \delta_n \Delta_n + \delta_n \widehat \Delta_n)^{2}/ (\Delta_{nl}\widehat\Delta_{nm})^2 \mid \F_n\right]$,
$\E \left[| f(\theta_n + \delta_n \Delta_n + \delta_n \widehat \Delta_n)/ (\Delta_{nl}\widehat\Delta_{nm})|^{2+\alpha_2} \mid \F_n\right]$,
%$\E \left[ f(\theta_n - \delta_n \Delta_n - \delta_n \widehat \Delta_n)^{2}/ (\Delta_{nl}\widehat\Delta_{nm})^2 \mid \F_n\right]$,
$\E \left[ |f(\theta_n - \delta_n \Delta_n - \delta_n \widehat \Delta_n)/ (\Delta_{nl}\widehat\Delta_{nm})|^{2+\alpha_2} \mid \F_n\right]$,
 $\E\left[\left. (\xi_n^+ + \xi_n^- - 2 \xi_n)^2/(\Delta_{nl}\widehat\Delta_{nm})^2 \right| \F_n \right] \le \alpha_1$ 
and $\E \left(\left\| \Upsilon(\overline H_n) \right\|^2 \mid \F_n\right) \le \alpha_1$. 
\item  $\delta_n = \frac{\delta_0}{(n+1)^{\varsigma}}$, where $\delta_0 > 0$ and $0 < \varsigma \le 1/8$.
\end{enumerate}
The reader is referred to Section II-B of \cite{prashanth2015rdsa} for a detailed discussion of the above assumptions. We remark here that (C14)-(C21) are identical to that in \cite{prashanth2015rdsa}, while (C22) and (C23) introduce minor additional requirements on $\left\| \Upsilon(\overline H_n \right\|^2$ and $\delta_n$, respectively and these are inspired by \cite{spall-jacobian}.

@@

We next present a convergence rate result for the special case of a quadratic objective function under the following additional assumptions:
\begin{enumerate}[label=(\textbf{C\arabic*}),resume]
\item  $f$ is quadratic and $\nabla^2 f(x^*) > 0$. 
\item The operator $\Upsilon$ is chosen such that $\E(\parallel \Upsilon(\overline H_n) - \overline H_n\parallel^2) = o(e^{-2wn^{1-r}/(1-r)})$ and $\parallel \Upsilon(H) - H \parallel^2 / (1+\parallel H \parallel^2)$ is uniformly bounded.
\end{enumerate}
\begin{theorem}(\textbf{2SPSA-3-IH Quadratic case - Convergence rate})
\label{thm:spsaquad-bound}
Assume (C17), (C23), (C24) and (C25) and also that the setting is noise-free. 
Let $b_n = b_0/n^r$, $n=1,2,\ldots,k$, where $1/2 < r < 1$ and $0 < b_0 \leq 1$. For notational simplicity, let $H^*=\nabla^2 f(x^*)$. Letting $\Lambda_k = \overline H_k - H^*$, we have 
\begin{align}
\text{trace}[\E (\Lambda_n \tr \Lambda_n)] = O(e^{-2b_0n^{1-r} / {1-r}}).
\label{eq:spsaquad-bigo}
\end{align}
\end{theorem}
\begin{proof}
Since the setting is noise-free with a quadratic objective, we can rewrite \eqref{eq:spsahnhat} as follows:
\begin{align}
 \widehat H_n =    \nabla^2 f(\theta_n) +\Psi_{n}(\nabla^2 f(\theta_n)),\label{eq:spsahnhat-ext}
\end{align}
where $\Psi_n(H)$ is defined in \eqref{eq:psinhatspsa3}.
The proof involves the following steps:
\begin{description}
  \item[Step 1:] Here we prove the MSE convergence of $\overline H_k$, i.e., $\E [\Lambda_n\tr \Lambda_n] \rightarrow 0$ a.s. as $n\rightarrow \infty$.
  \item[Step 2:] We unroll the recursion \eqref{eq:2spsa-3-ih} and then derive convenient representation for $\text{trace}[\E (\Lambda_n \tr \Lambda_n)]$.
  \item[Step 3:] We derive the main result in \eqref{eq:spsaquad-bigo} using a proof by contradiction. 
\end{description}
\noindent\textbf{Step 1: MSE convergence of $\overline H_n$} \\
This part in exactly the same manner as part (i) in Theorem 3 of \cite{spall-jacobian}.\\
\noindent\textbf{Step 2: Representation of $\text{trace}[\E (\Lambda_n \tr \Lambda_n)]$} \\
This part in exactly the same manner as part (ii) in Theorem 3 of \cite{spall-jacobian}.\\
\noindent\textbf{Step 3: The big-O result on $\text{trace}[\E (\Lambda_n \tr \Lambda_n)]$ convergence} \\
This part in exactly the same manner as part (iii) in Theorem 3 of \cite{spall-jacobian}.\\
\end{proof}

>>>>

 \chapter{Second-order SPSA-3 with improved hessian estimation (2SPSA-3-IH)}
\label{sec:2spsa-3-ih}
The second-order SPSA-3 with improved Hessian estimate performs an update iteration similar to that of 2RDSA-IH proposed in chapter \ref{sec:2rdsa-ih} (See \eqref{eq:e2rdsa} and \eqref{eq:2rdsa-H}). The main difference in the iterates is that 2SPSA-3-IH uses gradient and Hessian estimates according to \eqref{eq:grad-spsa} and \eqref{eq:2spsa-ber}. In this chapter we present the improvements to 2SPSA-3 Hessian recursion \eqref{eq:2spsa-3-ih} by incorporating a zero-mean feedback term and a general step-size. Note that though these ideas of improving the Hessian recursion are similar to the ideas presented in chapter \ref{sec:2rdsa-ih} for 2RDSA-IH, the derivation of the feedback term does not directly follow. We show that the proposed improvements to Hessian estimation in 2SPSA-3 are such  that the resulting 2SPSA-3-IH algorithm is provably convergent, in particular, the Hessian estimate $\overline H_n$ of 2SPSA-3-IH converges almost surely to the true Hessian. Moreover, we show, for the special case of a quadratic objective in noise-free setting, that the 2SPSA-3 scheme along with proposed improvement to Hessian estimation (henceforth referred to as 2SPSA-3-IH) results in a convergence rate that is on par with the corresponding rate for 2SPSA with Hessian estimation improvements (2SPSA-IH) \cite{spall-jacobian}. The advantage with 2SPSA-3-IH is that it requires only 75\% of the simulation cost per-iteration for 2SPSA-IH.

@@

Algorithm \ref{alg:spsa-3-ih-structure} presents the pseudocode and we describe the individual components of 2SPSA-3-IH below.
\section{Function evaluations}
Let $y_n$, $y_n^+$ and $y_n^-$ denote the function evaluations at $\theta_n$, $\theta_n+\delta_n \Delta_n+\delta_n \widehat \Delta_n$ and $\theta_n -\delta_n\Delta_n-\delta_n\widehat\Delta_n$ respectively, i.e., 
$y_n = f(\theta_n) + \xi_n$, $y_n^+ = f(\theta_n+\delta_n \Delta_n +\delta_n \widehat\Delta_n) + \xi_n^+$ and 
$y_n^- = f(\theta_n -\delta_n\Delta_n-\delta_n\widehat\Delta_n) + \xi_n^-$,
where the noise terms $\xi_n, \xi_n^+, \xi_n^-$ satisfy $\E\left[\left.\xi_n^+ + \xi_n^- - 2\xi_n \right| \F_n, \Delta_n, \widehat \Delta_n\right] = 0$ with $\F_n = \sigma(\theta_m,m <  n)$ denoting the underlying sigma-field.

@@

\section{Convergence analysis for 2SPSA-3-IH}
\label{sec:2spsa-results}
We make the same assumptions as those used in the analysis of \cite{prashanth2015rdsa}, with a few minor alterations. The assumptions are listed below:
\begin{pvn}
\item  The function
$f$ is four-times differentiable\footnote{Here $\nabla^4 f(\theta) = \dfrac{\partial^4 f (\theta)}{\partial \theta\tr \partial \theta\tr \partial \theta\tr \partial \theta\tr}$ denotes the fourth derivate of $f$ at $\theta$ and $\nabla^4_{i_1 i_2 i_3 i_4} f(\theta)$ denotes the $(i_1 i_2 i_3 i_4)$th entry of $\nabla^4 f(\theta)$, for $i_1, i_2, i_3,i_4=1,\ldots, N$.} with $\left|\nabla^4_{i_1 i_2 i_3 i_4} f(\theta) \right| < \infty$, for $i_1, i_2, i_3,i_4=1,\ldots, N$ and for all $\theta\in \R^N$.

@@

\item For any $\tau >0$ and nonempty $S \subseteq \{1,\ldots,N\}$, there exists a $\rho'(\tau,S)>\tau$ such that 
$$ \limsup_{n\rightarrow \infty} \left| \dfrac{\sum_{i \notin S} (\theta-\theta^*)_i \bar f_{ni}(\theta)}{\sum_{i \in S} (\theta-\theta^*)_i \bar f_{ni}(\theta)}               \right| < 1 \text{ a.s.}$$
for all $|(\theta-\theta^*)_i| < \tau$ when $i \notin S$ and $|(\theta-\theta^*)_i| \ge \rho'(\tau,S)$ when $i\in S$.
\item For some $\alpha_0, \alpha_1, \alpha_2 >0$ and for all $n,l,m$, $\E {\xi_n}^{2} \le \alpha_0$, $\E {\xi_n^{\pm}}^{2} \le \alpha_0$, $\E f(\theta_n)^{2} \le \alpha_1$,  $\E f(\theta_n + \delta_n \Delta_n + \delta_n \widehat \Delta_n)^{2},\E f(\theta_n - \delta_n \Delta_n - \delta_n \widehat \Delta_n)^{2} \le \alpha_1$, 
%$\E \left[ f(\theta_n + \delta_n \Delta_n + \delta_n \widehat \Delta_n)^{2}/ (\Delta_{nl}\widehat\Delta_{nm})^2 \mid \F_n\right]$,
$\E \left[| f(\theta_n + \delta_n \Delta_n + \delta_n \widehat \Delta_n)/ (\Delta_{nl}\widehat\Delta_{nm})|^{2+\alpha_2} \mid \F_n\right]$,
%$\E \left[ f(\theta_n - \delta_n \Delta_n - \delta_n \widehat \Delta_n)^{2}/ (\Delta_{nl}\widehat\Delta_{nm})^2 \mid \F_n\right]$,
$\E \left[ |f(\theta_n - \delta_n \Delta_n - \delta_n \widehat \Delta_n)/ (\Delta_{nl}\widehat\Delta_{nm})|^{2+\alpha_2} \mid \F_n\right]$,
 $\E\left[\left. (\xi_n^+ + \xi_n^- - 2 \xi_n)^2/(\Delta_{nl}\widehat\Delta_{nm})^2 \right| \F_n \right] \le \alpha_1$ 
and $\E \left(\left\| \Upsilon(\overline H_n) \right\|^2 \mid \F_n\right) \le \alpha_1$. 
\item  $\delta_n = \frac{\delta_0}{(n+1)^{\varsigma}}$, where $\delta_0 > 0$ and $0 < \varsigma \le 1/8$.
\end{pvn}
The reader is referred to Section II-B of \cite{prashanth2015rdsa} for a detailed discussion of the above assumptions. We remark here that (C14)-(C21) are identical to that in \cite{prashanth2015rdsa}, while (C22) and (C23) introduce minor additional requirements on $\left\| \Upsilon(\overline H_n \right\|^2$ and $\delta_n$, respectively and these are inspired by \cite{spall-jacobian}.

@@

We next present a convergence rate result for the special case of a quadratic objective function under the following additional assumptions:
\begin{pvn}
\item  $f$ is quadratic and $\nabla^2 f(x^*) > 0$. 
\item The operator $\Upsilon$ is chosen such that $\E(\parallel \Upsilon(\overline H_n) - \overline H_n\parallel^2) = o(e^{-2wn^{1-r}/(1-r)})$ and $\parallel \Upsilon(H) - H \parallel^2 / (1+\parallel H \parallel^2)$ is uniformly bounded.
\end{pvn}
\begin{theorem}(\textbf{2SPSA-3-IH Quadratic case - Convergence rate})
\label{thm:spsaquad-bound}
Assume (C17), (C23), (C24) and (C25) and also that the setting is noise-free. 
Let $b_n = b_0/n^r$, $n=1,2,\ldots,k$, where $1/2 < r < 1$ and $0 < b_0 \leq 1$. For notational simplicity, let $H^*=\nabla^2 f(x^*)$. Letting $\Lambda_k = \overline H_k - H^*$, we have 
\begin{align}
\text{trace}[\E (\Lambda_n \tr \Lambda_n)] = O(e^{-2b_0n^{1-r} / {1-r}}).
\label{eq:spsaquad-bigo}
\end{align}
\end{theorem}
\begin{proof}
Since the setting is noise-free with a quadratic objective, we can rewrite \eqref{eq:spsahnhat} as follows:
\begin{align}
 \widehat H_n =    \nabla^2 f(\theta_n) +\Psi_{n}(\nabla^2 f(\theta_n)),\label{eq:spsahnhat-ext}
\end{align}
where $\Psi_n(H)$ is defined in \eqref{eq:psinhatspsa3}.
The proof involves the following steps:
\begin{description}
  \item[Step 1:] Here we prove the MSE convergence of $\overline H_k$, i.e., $\E [\Lambda_n\tr \Lambda_n] \rightarrow 0$ a.s. as $n\rightarrow \infty$.
  \item[Step 2:] We unroll the recursion \eqref{eq:2spsa-3-ih} and then derive convenient representation for $\text{trace}[\E (\Lambda_n \tr \Lambda_n)]$.
  \item[Step 3:] We derive the main result in \eqref{eq:spsaquad-bigo} using a proof by contradiction. 
\end{description}
\noindent\textbf{Step 1: MSE convergence of $\overline H_n$} \\
This part in exactly the same manner as part (i) in Theorem 3 of \cite{spall-jacobian}.\\
\noindent\textbf{Step 2: Representation of $\text{trace}[\E (\Lambda_n \tr \Lambda_n)]$} \\
This part in exactly the same manner as part (ii) in Theorem 3 of \cite{spall-jacobian}.\\
\noindent\textbf{Step 3: The big-O result on $\text{trace}[\E (\Lambda_n \tr \Lambda_n)]$ convergence} \\
This part in exactly the same manner as part (iii) in Theorem 3 of \cite{spall-jacobian}.\\
\end{proof}

### 2017-01-17 secorder-rdsa-ih.tex
counter conditions problem resoved

The optimal choice for $b_n$ in \eqref{eq:2rdsa-H} is the following:
\begin{align}
\label{eq:wieghts}
b_i  = \delta_i^{4}/\sum\limits_{j=0}^{i} \delta_j^{4}.
\end{align}
The main idea behind the above choice is provided below.
From \eqref{eq:hnhat}, we can infer that
\begin{align*}
\E \parallel \widehat H_n \parallel^2 \le \dfrac{C}{\delta_n^4} \text{ for some } C<\infty. 
\end{align*} 
This is because the third term in \eqref{eq:hnhat} vanishes asymptotically, while the fourth term there dominates asymptotically. Moreover, the noise factors in the fourth term in \eqref{eq:hnhat} are bounded above due to (C9) and independent of $n$, leaving the $\delta_n^2$ term in the denominator there.

@@

\section{Convergence analysis}
\label{sec:2rdsa-results}
We make the same assumptions as those used in the analysis of \cite{prashanth2015rdsa}, with a few minor alterations. The assumptions are listed below:
\begin{enumerate}[label=(\textbf{A\arabic*}),resume]
\item  The function
$f$ is four-times differentiable\footnote{Here $\nabla^4 f(\theta) = \dfrac{\partial^4 f (\theta)}{\partial \theta\tr \partial \theta\tr \partial \theta\tr \partial \theta\tr}$ denotes the fourth derivate of $f$ at $\theta$ and $\nabla^4_{i_1 i_2 i_3 i_4} f(\theta)$ denotes the $(i_1, i_2, i_3, i_4)$th entry of $\nabla^4 f(\theta)$, for $i_1, i_2, i_3,i_4=1,\ldots, N$.} with $\left|\nabla^4_{i_1 i_2 i_3 i_4} f(\theta) \right| < \infty$, for $i_1, i_2, i_3,i_4=1,\ldots, N$ and for all $\theta\in \R^N$.

@@

\item For any $\tau >0$ and nonempty $S \subseteq \{1,\ldots,N\}$, there exists a $\rho'(\tau,S)>\tau$ such that 
$$ \limsup_{n\rightarrow \infty} \left| \dfrac{\sum_{i \notin S} (\theta-\theta^*)_i \bar f_{ni}(\theta)}{\sum_{i \in S} (\theta-\theta^*)_i \bar f_{ni}(\theta)}               \right| < 1 \text{ a.s.}$$
for all $|(\theta-\theta^*)_i| < \tau$ when $i \notin S$ and $|(\theta-\theta^*)_i| \ge \rho'(\tau,S)$ when $i\in S$.
\item For some $\alpha_0, \alpha_1>0$ and for all $n$, $\E {\xi_n}^{2} \le \alpha_0$, $\E {\xi_n^{\pm}}^{2} \le \alpha_0$, $\E f(\theta_n)^{2} \le \alpha_1$,  $\E f(\theta_n\pm \delta_n d_n)^{2} \le \alpha_1$ and $\E \left(\left\| \Upsilon(\overline H_n) \right\|^2 \mid \F_n\right) \le \alpha_1$. 
\item  $\delta_n = \frac{\delta_0}{(n+1)^{\varsigma}}$, where $\delta_0 > 0$ and $0 < \varsigma \le 1/8$.
\end{enumerate}
The reader is referred to Section II-B of \cite{prashanth2015rdsa} for a detailed discussion of the above assumptions. We remark here that (C1)-(C8) are identical to assumptions in \cite{prashanth2015rdsa}, while (C9) and (C10) introduce minor additional requirements on $\left\| \Upsilon(\overline H_n \right\|^2$ and $\delta_n$, respectively and these are inspired from \cite{spall-jacobian}.

\begin{lemma}(\textbf{Bias in Hessian estimate})
\label{lemma:2rdsa-bias}
Under (C1)-(C10), with $\widehat H_n$ defined according to \eqref{eq:2rdsa-estimate-ber}, we have a.s. that\footnote{Here $\widehat H_n(i,j)$ and $\nabla^2_{ij}f(\cdot)$ denote the $(i,j)$th entries in the Hessian estimate $\widehat H_n$ and the true Hessian $\nabla^2 f(\cdot)$, respectively.}, for $i,j = 1,\ldots,N$,
\begin{align}
\left|\E\left[
\left. \widehat H_n(i,j) \right| \F_n \right] - \nabla^2_{ij} f(\theta_n)\right| = O(\delta_n^2).
\end{align} 
\end{lemma}
\begin{proof}
See Lemma 4 in \cite{prashanth2015rdsa}.
\end{proof}

\begin{theorem}(\textbf{Strong Convergence of Hessian})
\label{thm:2rdsa-H}
Under (C1)-(C10), we have that 
$$\theta_n \rightarrow \theta^*, \overline H_n \rightarrow \nabla^2 f(\theta^*) \text{ a.s. as } n\rightarrow \infty.$$ 
In the above, $\theta_n$ and $\overline H_n$ are updated according to \eqref{eq:e2rdsa} and \eqref{eq:2rdsa-H}, respectively, $\widehat H_n$ is defined according to \eqref{eq:2rdsa-estimate-ber} and the step-sizes $b_n$ are chosen as suggested in \eqref{eq:wieghts}. 
\end{theorem}
\begin{proof}
The first part of the claim regarding $\theta_n$ follows in exactly the same fashion as the proof of Theorem 5 in \cite{prashanth2015rdsa}.  
For proving the claim regarding $\overline H_n$, we closely follow the approach used to prove a corresponding result for 2SPSA (see Theorem 1 in \cite{spall-jacobian}). 
The first step is to prove the following:
\begin{align}
\sum_{k=0}^n \dfrac{\delta_k^4 \left(\widehat H_k - \widehat \Psi_k - \E(\widehat H_k \mid \F_k)\right)}{\sum_{i=0}^n \delta_i^4} \rightarrow 0.
\label{eq:step1}
\end{align}

>>>>

The optimal choice for $b_n$ in \eqref{eq:2rdsa-H} is the following:
\begin{align}
\label{eq:wieghts}
b_i  = \delta_i^{4}/\sum\limits_{j=0}^{i} \delta_j^{4}.
\end{align}
The main idea behind the above choice is provided below.
From \eqref{eq:hnhat}, we can infer that
\begin{align*}
\E \parallel \widehat H_n \parallel^2 \le \dfrac{C}{\delta_n^4} \text{ for some } C<\infty. 
\end{align*} 
This is because the third term in \eqref{eq:hnhat} vanishes asymptotically, while the fourth term there dominates asymptotically. Moreover, the noise factors in the fourth term in \eqref{eq:hnhat} are bounded above due to (A16) and independent of $n$, leaving the $\delta_n^2$ term in the denominator there.

@@

\section{Convergence analysis}
\label{sec:2rdsa-results}
We make the same assumptions as those used in the analysis of \cite{prashanth2015rdsa}, with a few minor alterations. The assumptions are listed below:
\begin{pvn}
\item  The function
$f$ is four-times differentiable\footnote{Here $\nabla^4 f(\theta) = \dfrac{\partial^4 f (\theta)}{\partial \theta\tr \partial \theta\tr \partial \theta\tr \partial \theta\tr}$ denotes the fourth derivate of $f$ at $\theta$ and $\nabla^4_{i_1 i_2 i_3 i_4} f(\theta)$ denotes the $(i_1, i_2, i_3, i_4)$th entry of $\nabla^4 f(\theta)$, for $i_1, i_2, i_3,i_4=1,\ldots, N$.} with $\left|\nabla^4_{i_1 i_2 i_3 i_4} f(\theta) \right| < \infty$, for $i_1, i_2, i_3,i_4=1,\ldots, N$ and for all $\theta\in \R^N$.

@@

\item For any $\tau >0$ and nonempty $S \subseteq \{1,\ldots,N\}$, there exists a $\rho'(\tau,S)>\tau$ such that 
$$ \limsup_{n\rightarrow \infty} \left| \dfrac{\sum_{i \notin S} (\theta-\theta^*)_i \bar f_{ni}(\theta)}{\sum_{i \in S} (\theta-\theta^*)_i \bar f_{ni}(\theta)}               \right| < 1 \text{ a.s.}$$
for all $|(\theta-\theta^*)_i| < \tau$ when $i \notin S$ and $|(\theta-\theta^*)_i| \ge \rho'(\tau,S)$ when $i\in S$.
\item For some $\alpha_0, \alpha_1>0$ and for all $n$, $\E {\xi_n}^{2} \le \alpha_0$, $\E {\xi_n^{\pm}}^{2} \le \alpha_0$, $\E f(\theta_n)^{2} \le \alpha_1$,  $\E f(\theta_n\pm \delta_n d_n)^{2} \le \alpha_1$ and $\E \left(\left\| \Upsilon(\overline H_n) \right\|^2 \mid \F_n\right) \le \alpha_1$. 
\item  $\delta_n = \frac{\delta_0}{(n+1)^{\varsigma}}$, where $\delta_0 > 0$ and $0 < \varsigma \le 1/8$.
\end{pvn}
The reader is referred to Section II-B of \cite{prashanth2015rdsa} for a detailed discussion of the above assumptions. We remark here that (A8)-(A15) are identical to assumptions in \cite{prashanth2015rdsa}, while (A16) and (A17) introduce minor additional requirements on $\left\| \Upsilon(\overline H_n \right\|^2$ and $\delta_n$, respectively and these are inspired from \cite{spall-jacobian}.

\begin{lemma}(\textbf{Bias in Hessian estimate})
\label{lemma:2rdsa-bias}
Under (A8)-(A17), with $\widehat H_n$ defined according to \eqref{eq:2rdsa-estimate-ber}, we have a.s. that\footnote{Here $\widehat H_n(i,j)$ and $\nabla^2_{ij}f(\cdot)$ denote the $(i,j)$th entries in the Hessian estimate $\widehat H_n$ and the true Hessian $\nabla^2 f(\cdot)$, respectively.}, for $i,j = 1,\ldots,N$,
\begin{align}
\left|\E\left[
\left. \widehat H_n(i,j) \right| \F_n \right] - \nabla^2_{ij} f(\theta_n)\right| = O(\delta_n^2).
\end{align} 
\end{lemma}
\begin{proof}
See Lemma 4 in \cite{prashanth2015rdsa}.
\end{proof}

\begin{theorem}(\textbf{Strong Convergence of Hessian})
\label{thm:2rdsa-H}
Under (A8)-(A17), we have that 
$$\theta_n \rightarrow \theta^*, \overline H_n \rightarrow \nabla^2 f(\theta^*) \text{ a.s. as } n\rightarrow \infty.$$ 
In the above, $\theta_n$ and $\overline H_n$ are updated according to \eqref{eq:e2rdsa} and \eqref{eq:2rdsa-H}, respectively, $\widehat H_n$ is defined according to \eqref{eq:2rdsa-estimate-ber} and the step-sizes $b_n$ are chosen as suggested in \eqref{eq:wieghts}. 
\end{theorem}
\begin{proof}
The first part of the claim regarding $\theta_n$ follows in exactly the same fashion as the proof of Theorem 5 in \cite{prashanth2015rdsa}.  
For proving the claim regarding $\overline H_n$, we closely follow the approach used to prove a corresponding result for 2SPSA (see Theorem 1 in \cite{spall-jacobian}). 
The first step is to prove the following:
\begin{align}
\sum_{k=0}^n \dfrac{\delta_k^4 \left(\widehat H_k - \widehat \Psi_k - \E(\widehat H_k \mid \F_k)\right)}{\sum_{i=0}^n \delta_i^4} \rightarrow 0.
\label{eq:step1}
\end{align}
